Sustainable Indicators

### 2020-12-15 02-supply-chain.Rmd
add ref

---
title: "Sustainable Indicators"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
#bibliography: Biblio.bib
#nocite: '@*'

@@

>>>>

---
title: "Sustainable Indicators"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
bibliography: 02-supply-chain.bib
#nocite: '@*'

@@

## Rational

- @Alkhuzaim2020 provide insights into more effective environmentally sustainable supply chain and circularity performance evaluation, accounting, and appraisal using emergy based performance measurements.
